simResults_svm

### 2024-08-01 sim_4.enet/simResults_enet.Rmd
sim results by enet, svm did not run svm, long running time

  proxy_enet.i <- paste0("proxy_enet.", i)
  assign(proxy_enet.i, proxy_enet)
  sum.RD_enet.i <- paste0("sum.RD_enet.", i)
  assign(sum.RD_enet.i, sum.RD_enet)
}
```
```{r scenarioER: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
set.seed(42)

>>>>

  proxy_enet.i <- paste0("proxy_enet.", i)
  assign(proxy_enet.i, proxy_enet)
  sum.RD_enet.i <- paste0("sum.RD_enet.", i)
  assign(sum.RD_enet.i, sum.RD_enet)
}
```

```{r scenarioER: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
set.seed(42)

### 2024-08-01 sim_5.svm/simResults_svm.Rmd
sim results by enet, svm did not run svm, long running time

---
title: "simResults_enet"
author: "Yang Lei"
date: "2024-08-01"
output: html_document
---

@@

RD_enet <- data.frame(RD = numeric(),
                       SE = numeric())
```

```{r scenario: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
set.seed(42)

@@

  enet.fit <- glmnet::cv.glmnet(y = data$outcome, 
                                 x = covar.mat, 
                                 type.measure='mse',
                                 family="binomial",
                                 alpha = 0.5, 
                                 nfolds = 5)
  coef.fit <- coef(enet.fit,s='lambda.min',exact=TRUE)
  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
  proxy_enet <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_enet, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_enet <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_enet$ps
  data$w.l <- W.out_enet$weights

  fit.OR_enet <- glm(out.formula,
                      data = data,
                      weights = W.out_enet$weights,
                      family= binomial(link = "logit"))
  fit.RD_enet <- glm(out.formula,
                       data = data,
                       weights = W.out_enet$weights,
                       family = gaussian(link= "identity"))
  sum.RD_enet <- c(summary(fit.RD_enet)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_enet)[2,2]))

  RD_enet[i,] <- sum.RD_enet
  rownames(RD_enet)[i] <- paste0("data.", i, "_enet")

  proxy_enet.i <- paste0("proxy_enet.", i)
  assign(proxy_enet.i, proxy_enet)
  sum.RD_enet.i <- paste0("sum.RD_enet.", i)
  assign(sum.RD_enet.i, sum.RD_enet)
}
```

```{r scenarioER: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
set.seed(42)

@@

  enet.fit <- glmnet::cv.glmnet(y = data$outcome, 
                                 x = covar.mat, 
                                 type.measure='mse',
                                 family="binomial",
                                 alpha = 1, 
                                 nfolds = 5)
  coef.fit <- coef(enet.fit,s='lambda.min',exact=TRUE)
  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
  proxy_enet <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_enet, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_enet <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_enet$ps
  data$w.l <- W.out_enet$weights

  fit.OR_enet <- glm(out.formula,
                      data = data,
                      weights = W.out_enet$weights,
                      family= binomial(link = "logit"))
  fit.RD_enet <- glm(out.formula,
                       data = data,
                       weights = W.out_enet$weights,
                       family = gaussian(link= "identity"))
  sum.RD_enet <- c(summary(fit.RD_enet)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_enet)[2,2]))

  RD_enet[i+a,] <- sum.RD_enet
  rownames(RD_enet)[i+a] <- paste0("ER.data.", i, "_enet")

  proxy_enet.i <- paste0("proxy_enet.ER.", i)
  assign(proxy_enet.i, proxy_enet)
  sum.RD_enet.i <- paste0("sum.RD_enet.ER.", i)
  assign(sum.RD_enet.i, sum.RD_enet)
}
```

```{r scenarioOR: for-loop generating RD & SE results for enet, warning=FALSE, cache=TRUE}
set.seed(42)

@@

  enet.fit <- glmnet::cv.glmnet(y = data$outcome, 
                                 x = covar.mat, 
                                 type.measure='mse',
                                 family="binomial",
                                 alpha = 1, 
                                 nfolds = 5)
  coef.fit <- coef(enet.fit,s='lambda.min',exact=TRUE)
  sel.variables <- row.names(coef.fit)[which(as.numeric(coef.fit)!=0)]
  proxy_enet <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_enet, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_enet <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")
  #
  data$ps.l <- W.out_enet$ps
  data$w.l <- W.out_enet$weights

  fit.OR_enet <- glm(out.formula,
                      data = data,
                      weights = W.out_enet$weights,
                      family= binomial(link = "logit"))
  fit.RD_enet <- glm(out.formula,
                       data = data,
                       weights = W.out_enet$weights,
                       family = gaussian(link= "identity"))
  sum.RD_enet <- c(summary(fit.RD_enet)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_enet)[2,2]))

  RD_enet[i+2*a,] <- sum.RD_enet
  rownames(RD_enet)[i+2*a] <- paste0("OR.data.", i, "_enet")

  proxy_enet.i <- paste0("proxy_enet.OR.", i)
  assign(proxy_enet.i, proxy_enet)
  sum.RD_enet.i <- paste0("sum.RD_enet.OR.", i)
  assign(sum.RD_enet.i, sum.RD_enet)
}
```

```{r read RD & SE results by enet, warning=FALSE, cache=TRUE}
RD_enet
```

```{r check intermediate results for each data by enet, warning=FALSE, cache=TRUE}
# check RD & SE by enet for each data, print:
#   sum.RD_enet.n, sum.RD_enet.ER.n, or sum.RD_enet.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
sum.RD_enet.1
sum.RD_enet.ER.2

# check proxy selected by enet for each data, print:
#   proxy_enet.n, proxy_enet.ER.n, or proxy_enet.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_enet.1
proxy_enet.ER.3
```

>>>>

---
title: "simResults_svm"
author: "Yang Lei"
date: "2024-08-01"
output: html_document
---

@@

RD_svm <- data.frame(RD = numeric(),
                       SE = numeric())
```

```{r scenario: for-loop generating RD & SE results for svm, warning=FALSE, cache=TRUE}
set.seed(42)

@@

  svmTrainOutcome <- data$outcome
  svmTrainOutcome[svmTrainOutcome == 0] <- -1
  svmTrainPreds <- data.frame(covar.mat)

  bounds <- t(data.frame(log2lambda1=c(-10, 10), log2lambda2=c(-10,10)))
  colnames(bounds)<-c("lower", "upper")
  svm.model <- svmfs(x=covar.mat,
                     y = svmTrainOutcome,
                     fs.method = "scad+L2",
                     bounds=bounds,
                     grid.search = "interval",
                     inner.val.method = "cv",
                     show = "none",
                     parms.coding = "none",
                     seed=42)

  sel.variables <- colnames(covar.mat)[svm.model$model$fit.info$model.list$model$xind]
  proxy_svm <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_svm, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_svm <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")

  data$ps.l <- W.out_svm$ps
  data$w.l <- W.out_svm$weights

  fit.OR_svm <- glm(out.formula,
                      data = data,
                      weights = W.out_svm$weights,
                      family= binomial(link = "logit"))
  fit.RD_svm <- glm(out.formula,
                       data = data,
                       weights = W.out_svm$weights,
                       family = gaussian(link= "identity"))
  sum.RD_svm <- c(summary(fit.RD_svm)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_svm)[2,2]))

  RD_svm[i,] <- sum.RD_svm
  rownames(RD_svm)[i] <- paste0("data.", i, "_svm")

  proxy_svm.i <- paste0("proxy_svm.", i)
  assign(proxy_svm.i, proxy_svm)
  sum.RD_svm.i <- paste0("sum.RD_svm.", i)
  assign(sum.RD_svm.i, sum.RD_svm)
}
```

```{r scenarioER: for-loop generating RD & SE results for svm, warning=FALSE, cache=TRUE}
set.seed(42)

@@

  svmTrainOutcome <- data$outcome
  svmTrainOutcome[svmTrainOutcome == 0] <- -1
  svmTrainPreds <- data.frame(covar.mat)

  bounds <- t(data.frame(log2lambda1=c(-10, 10), log2lambda2=c(-10,10)))
  colnames(bounds)<-c("lower", "upper")
  svm.model <- svmfs(x=covar.mat,
                     y = svmTrainOutcome,
                     fs.method = "scad+L2",
                     bounds=bounds,
                     grid.search = "interval",
                     inner.val.method = "cv",
                     show = "none",
                     parms.coding = "none",
                     seed=42)

  sel.variables <- colnames(covar.mat)[svm.model$model$fit.info$model.list$model$xind]
  proxy_svm <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_svm, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_svm <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")

  data$ps.l <- W.out_svm$ps
  data$w.l <- W.out_svm$weights

  fit.OR_svm <- glm(out.formula,
                      data = data,
                      weights = W.out_svm$weights,
                      family= binomial(link = "logit"))
  fit.RD_svm <- glm(out.formula,
                       data = data,
                       weights = W.out_svm$weights,
                       family = gaussian(link= "identity"))
  sum.RD_svm <- c(summary(fit.RD_svm)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_svm)[2,2]))

  RD_svm[i+a,] <- sum.RD_svm
  rownames(RD_svm)[i+a] <- paste0("ER.data.", i, "_svm")

  proxy_svm.i <- paste0("proxy_svm.ER.", i)
  assign(proxy_svm.i, proxy_svm)
  sum.RD_svm.i <- paste0("sum.RD_svm.ER.", i)
  assign(sum.RD_svm.i, sum.RD_svm)
}
```

```{r scenarioOR: for-loop generating RD & SE results for svm, warning=FALSE, cache=TRUE}
set.seed(42)

@@

  svmTrainOutcome <- data$outcome
  svmTrainOutcome[svmTrainOutcome == 0] <- -1
  svmTrainPreds <- data.frame(covar.mat)

  bounds <- t(data.frame(log2lambda1=c(-10, 10), log2lambda2=c(-10,10)))
  colnames(bounds)<-c("lower", "upper")
  svm.model <- svmfs(x=covar.mat,
                     y = svmTrainOutcome,
                     fs.method = "scad+L2",
                     bounds=bounds,
                     grid.search = "interval",
                     inner.val.method = "cv",
                     show = "none",
                     parms.coding = "none",
                     seed=42)

  sel.variables <- colnames(covar.mat)[svm.model$model$fit.info$model.list$model$xind]
  proxy_svm <- proxy.list[proxy.list %in% sel.variables]
  proxyform <- paste0(proxy_svm, collapse = "+")
  rhsform <- paste0(c(covform, proxyform), collapse = "+")
  ps.formula <- as.formula(paste0("exposure", "~", rhsform))

  W.out_svm <- weightit(ps.formula, 
                          data = data, 
                          estimand = "ATE",
                          method = "ps")

  data$ps.l <- W.out_svm$ps
  data$w.l <- W.out_svm$weights

  fit.OR_svm <- glm(out.formula,
                      data = data,
                      weights = W.out_svm$weights,
                      family= binomial(link = "logit"))
  fit.RD_svm <- glm(out.formula,
                       data = data,
                       weights = W.out_svm$weights,
                       family = gaussian(link= "identity"))
  sum.RD_svm <- c(summary(fit.RD_svm)$coef["exposure", c("Estimate")], sqrt(sandwich::sandwich(fit.RD_svm)[2,2]))

  RD_svm[i+2*a,] <- sum.RD_svm
  rownames(RD_svm)[i+2*a] <- paste0("OR.data.", i, "_svm")

  proxy_svm.i <- paste0("proxy_svm.OR.", i)
  assign(proxy_svm.i, proxy_svm)
  sum.RD_svm.i <- paste0("sum.RD_svm.OR.", i)
  assign(sum.RD_svm.i, sum.RD_svm)
}
```

```{r read RD & SE results by svm, warning=FALSE, cache=TRUE}
RD_svm
```

```{r check intermediate results for each data by svm, warning=FALSE, cache=TRUE}
# check RD & SE by svm for each data, print:
#   sum.RD_svm.n, sum.RD_svm.ER.n, or sum.RD_svm.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
sum.RD_svm.1
sum.RD_svm.ER.2

# check proxy selected by svm for each data, print:
#   proxy_svm.n, proxy_svm.ER.n, or proxy_svm.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_svm.1
proxy_svm.ER.3
```
